|

### 2021-09-15 03-Chp-Systematic-Review.Rmd
Still copying data across to new format

Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO CITATION NEEDED --> <!-- TODO do i actually want to include MCI? --> For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

@@

@@

@@

@@

@@

Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable. This was not feasible in the context of this review, given the large number of records to be screened, even when using study design filters (n=`r comma(16109)`). Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated. Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substanital benefit.

@@

>>>>

Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. <!-- TODO CITATION NEEDED --> <!-- TODO do i actually want to include MCI? -->

__Bit on inclusion of EHR, where it is unclear how dementia diagnosed.__

<!-- TODO Any study using EHR - go back and extract codelists -->

For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

@@

##

@@

<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->

Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.

@@

<!-- TODO Check inclusion of Rockwood 2002:  -->

@@

One of the strenghts of this review is it's inclusion of MR studies as a source of evidence.

@@

Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable. This was not feasible in the context of this review, given the large number of records to be screened, even when using study design filters (n=`r comma(16109)`). Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated. Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substantial benefit.

@@

Talk about problem with studies sharing underlying datasets in two sample MR frameworks - c.f. EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, MR analysis can be multiple studies using the exact same summary statistics from the same cohorts

Introduce assumptions underlying MR (with image). Higlight that most if not all included analysis initially describing a protective effect of LDL-c, which attenuates to the NULL once ApoE4 gene regions are removed. Note the region must be quite wide - talk about controversy surrounding Benn paper

MR are limited by the need for SNP to be present in both datasets (for TSMR).

Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of exisitng GWASes to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here. -->
